RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-28 assets/illustration/equivalent_circuit.tex
:paintbrush: Update illustrations
:mag: Update notations

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\Large]
	\draw (0,0) coordinate(O)
	to [sV,l=$V_0$] ++(0,1.5)
	to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
	to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
	to [sI,l_=$I_0$,-*] ++(0,-3)
	to [short] (O);
	\draw (AM)
	to [short] ++(0.5,0)
	to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
	to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
	\draw (M)
	to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
	\draw (MH)
	to [D,-*] ++(1.5,0) coordinate(H)
	to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
	\draw (H)
	to [short] ++(1.5,0)
	to [R=$R_{\mathrm{H}}$] ++(0,-3)
	to [short] (O);

	\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
	\draw [red,dashed] (4,-0.5) rectangle (9,4);
	\draw [brown,dashed] (9.5,-0.5) rectangle (13.5,4);

	\draw [blue] (1.125,4.25) node[]{Antenna};
	\draw [red] (6.5,4.25) node[]{Modulator};
	\draw [brown] (11.5,4.25) node[]{Harvester \& Chip};

	\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
	\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
	\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
\end{circuitikz}

>>>>

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\Large]
	\draw (0,0) coordinate(O)
	to [sV,l=$V_0$] ++(0,1.5)
	to [L,l=$X_{\text{A}}$] ++(0,1.5)
	to [R=$R_{\text{A}}$,-*] ++(3,0) coordinate(AM)
	to [sI,l_=$I_0$,-*] ++(0,-3)
	to [short] (O);
	\draw (AM)
	to [short] ++(0.5,0)
	to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
	to [R=$R_{\text{S},m}$] ++(3,0) coordinate(MH);
	\draw (M)
	to [R=$R_{\text{P},m}$,-*] ++(0,-3);
	\draw (MH)
	to [D,-*] ++(1.5,0) coordinate(H)
	to [C=$X_{\text{H}}$,-*] ++(0,-3);
	\draw (H)
	to [short] ++(1.5,0)
	to [R=$R_{\text{H}}$] ++(0,-3)
	to [short] (O);

	\draw [dashed] (-1.125,-0.5) rectangle (3.5,4);
	\draw [dashed] (4,-0.5) rectangle (9,4);
	\draw [dashed] (9.5,-0.5) rectangle (13.5,4);

	\draw (1.125,4.25) node[]{Antenna};
	\draw (6.5,4.25) node[]{Modulator};
	\draw (11.5,4.25) node[]{Harvester \& Chip};

	\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\text{A}}$] (3.125,3.175);
	\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
	\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\text{H}}$] (9.875,0.375);
\end{circuitikz}

### 2022-11-28 assets/illustration/scatter_model.tex
:truck: Move assets
:paintbrush: Update scatter model
:mag: Update notations

% \begin{circuitikz}[transform shape]
% 	\tikzstyle{every node}=[font=\Large]
% 	\draw (0,0) node[bareantenna](bareantenna){};
% 	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
% 	\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
% 	\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
% 	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
% 	\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
% 	\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
% 	\draw (bareantenna)
% 	to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
% 	\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
% 	to [R=$Z_m$] ++(2,0) node[ground]{};
% \end{circuitikz}

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\large]
	\draw (0,0) node[bareantenna](bareantenna){};
	\draw (bareantenna.west) ++(-1,0) node[waves](WI){};
	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
	\draw (bareantenna.east) ++(0.5,0) node[waves](WR){};
	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E3);
	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E4);
	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
	\draw (E1) to[short,-*] (E2);
	\draw (E2) to[short,-*] (E3);
	% \draw (E2) to[short,-*] (E);
	% \draw (E) to[short,-*] (E3);
	\draw (E3) to[short] (E4);
	\draw (E2) to[short] ++(0.2,0) node[ground,rotate=90]{};
\end{circuitikz}

>>>>

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\large]
	\ctikzset{multipoles/rotary/arrow=both}
	\draw (0,0) node[bareantenna](bareantenna){};
	\draw (bareantenna.west) ++(-1,0) node[waves](WI){};
	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\text{I}}$};
	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\text{I}}$};
	\draw (bareantenna.east) ++(0.5,0) node[waves](WR){};
	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\text{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E3);
	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E4);
	\draw (E1) to[short,-*] (E2);
	\draw (E2) to[short,-*] (E3);
	\draw (E3) to[short] (E4);
	\draw (E2) to[short] ++(0.2,0) node[ground,rotate=90]{};
\end{circuitikz}
